Figure 1 - overview

### 2024-08-08 ms_figure_1_overview.Rmd
Remove tick marks Fig1

fig1c <- ggdraw() + 
    draw_image("schematics/Fig1C_placeholder_screen_overview_Arial.png")

cowplot::plot_grid(
    fig1c,
    cowplot::plot_grid(
        gg_dbd, 
        gg_tpm + geom_segment(data = ave_tpm |> filter(bait %in% c("mei4", "atf31", "atf21", "cuf2", "rsv1")),
                              aes(x = bait, xend = bait, y = -6, yend = -20), color = main_colors[1], 
                              linewidth = 1.25) + 
            scale_y_continuous(expand = expansion(mult = c(0, 0.025))) + 
            theme(axis.text.x = element_blank()),
        nrow = 1,
        labels = c("B", "C"),
        align = "vh",
        axis = "b"
    ),
    cowplot::plot_grid(
        gg_nbrint,
        gg_nbrpeaks_all_narrow_by_npeaks,
        nrow = 1, 
        labels = c("D", "E"),
        align = "vh", 
        axis = "b"
    ),
    nrow = 3,
    labels = c("A", NA, NA),
    align = "v",
    axis = "b",
    rel_heights = c(73, 50, 50)
)
```

>>>>

fig1c <- ggdraw() + 
    draw_image("schematics/Fig1A_placeholder_screen_overview_Arial.png")

cowplot::plot_grid(
    fig1c,
    cowplot::plot_grid(
        gg_dbd, 
        gg_tpm + geom_segment(data = ave_tpm |> filter(bait %in% c("mei4", "atf31", "atf21", "cuf2", "rsv1")),
                              aes(x = bait, xend = bait, y = -6, yend = -20), color = main_colors[1], 
                              linewidth = 1.25) + 
            scale_y_continuous(expand = expansion(mult = c(0, 0.025))) + 
            theme(axis.text.x = element_blank(),
                  axis.ticks.length.x = unit(0, "mm")),
        nrow = 1,
        labels = c("B", "C"),
        align = "vh",
        axis = "b"
    ),
    cowplot::plot_grid(
        gg_nbrint,
        gg_nbrpeaks_all_narrow_by_npeaks,
        nrow = 1, 
        labels = c("D", "E"),
        align = "vh", 
        axis = "b"
    ),
    nrow = 3,
    labels = c("A", NA, NA),
    align = "v",
    axis = "b",
    rel_heights = c(73, 50, 50)
)
```
